---
title: "Topology of a reservoir network with HydroSHEDS"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(sf,warn.conflicts=FALSE)
library(assimReservoirs,warn.conflicts=FALSE)
library(dplyr,warn.conflicts=FALSE)
library(igraph,warn.conflicts=FALSE)
library(knitr,warn.conflicts=FALSE)
library(ggplot2,warn.conflicts=FALSE)
```

# Global datasets of rivers and reservoirs

## Rivers

We use HydroSHEDS as a consistent global river dataset. The resolution is about 90 m around the equator (3 arc-seconds).

> Lehner, B., Verdin, K., Jarvis, A. (2008): New global hydrography derived from spaceborne elevation data. Eos, Transactions, AGU, 89(10): 93-94.

For example in Ceará:

```{r, results='asis'}
plot(riv["UP_CELLS"])

# ggplot(riv) + geom_sf(aes(color=UP_CELLS))

```

Since the river network dataset of HydroSHEDS has valid topology, we can operate on it with package `igraph`, using graph theory. We can for example obtain __all disjoint components of the graph__:

```{r}
riv_split = split_river_network(riv)
plot(riv_split["membership"])

split_river_network

```

Selecting a reach somewhere within the Jaguaribe river basin:

```{r}
reach_id=140877
riv_jagua = select_disjoint_river(reach_id,riv_split)
plot(riv_i["UP_CELLS"])
```


## Reservoirs

We use the JRC global surface water dataset.

> Jean-Francois Pekel, Andrew Cottam, Noel Gorelick, Alan S. Belward, High-resolution mapping of global surface water and its long-term changes. Nature 540, 418-422 (2016). (doi:10.1038/nature20584)

Resolution is 30 m. We run `allocate_reservoir_to_river(riv)`, `Routing()` and `Routing_non_strat()` in advance in order to create a graph. Then we can obtain any

### Small example with reservoir with `r id='34560'`

Evaluate all reservoirs downstream of selected:

```{r}
id='34560'

neighbors(reservoir_graph,id,'in')
sub=all_simple_paths(reservoir_graph,from=id,mode='in') %>%
  unlist %>%
  unique

Vsubgraph = induced_subgraph(reservoir_graph, sub ,impl='auto')

plot(Vsubgraph)

vertices = V(Vsubgraph)  

res_subgraph = filter(res_max,res_max$id_jrc %in% vertices$name)

reach_id = filter(res_subgraph,`id_jrc`==id) %>% pull(`nearest river`)
riv_upstr=river_upstream(reach_id,riv,river_graph)

ggplot(res_subgraph %>% mutate(`nearest river`=as.factor(`nearest river`))) + geom_sf(aes(color=`nearest river`)) + geom_sf(data=riv_upstr)




```
